{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-04-28 draft.tex
Revised the introduction and todo list.

%%%%%%%%% ABSTRACT
\begin{abstract}

\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

\begin{comment}
Maybe the goal of this work is to publish a journal paper about a
practical solution for a drone to follow a single target. For this, we
need some descriptions on
\begin{itemize}
\item A vision-based, single target tracking algorithm.
\item Other components for making a drone follow a target.
\begin{itemize}
\item An architecture diagram
\item Descriptions of vehicle control, motion planning, behavior
  generation, estimation of relative geometry between a drone and a
  target, etc
\item Experimental results or example videos
\end{itemize}
\end{itemize}

For the BMVC-17 submission, we're going to just focus on the first
part -- a vision-based, single target tracking algorithm. This is
because we need to build a drone for the second part.
\end{comment}

\begin{comment}
\begin{itemize}
\item Introduction: Should talk about, at least, motivation of this
  work, brief review of the literature, and contribution
\item Method: Detail the method w.r.t. a diagram of system
  architecture or pseudo code
\begin{itemize}
\item Kernelized Correlation Filter
\item A variant of KCF: Multiple KCF w/ PF ({\it E}nKCF, ${\it E}nKCF_{+RD}$
\item Re-detection for re-initialization: Modules for reliably
  detecting target-lost, for extensively searching the lost target,
  and for picking up the same target with a help from an appearance
  model or other models.
\begin{itemize}
\item To filter out unlikely box proposals,
\begin{itemize}
\item Use a prior information about box, our outputs, dimensions
  (e.g., a combination of width and height, aspect ratio, etc.)
\item Use the information about the trajectory of the target before we
  lose the target.
\end{itemize}
\item MTH: revisited
\item To make a box tighter, generate our own box proposals based on
  the locations of top $k$ box proposals from object proposal methods,
  e.g., Edge Box.
\end{itemize}
\end{itemize}
\item Experiment: Detail the data, and experimental setup; results and findings
\item Will compare the performance of {\it E}nKCF, Naive{\it E}nKCF,
  ${\it E}nKCF_{+RD}$ with those of the following tracking methods.
\begin{itemize}
\item vanilla-KCF w/ a fixed scale,
\item vanilla-KCF w/ three different scales,
\item LCT (Long-term Correlation Tracking) \cite{ma2015long}: Temporal
  correlation of a target over frames; a pyramid for different scales;
  re-detection w/ an appearance classifier (i.e., a naive Bayes w/
  random fern features in combination of sliding window). Temporal
  context regressor for translation over significant deformation and
  target regressor for scale variation.
\item MEEM (Multiple Experts using Entropy Minimization)
  \cite{zhang2014meem}.
\item SAMF (Scale Adaptive KCF)
\item STC (fast tracking via Spatio-Temporal Context learning)
  \cite{zhang2014fast}: 
\item Struck (Structured Output Tracking with Kernels)
\end{itemize}
\begin{itemize}
\item Visual tracker benchmark (VTB)
\item DTB-70: w/ and w/o motion estimation,
\item UAV123 \footnote{A set of images acquired from an UAV is called
  ``UAV123'' and publicly available from
  https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}
\item VOT
\end{itemize}
\item Conclusion
\end{itemize}
\end{comment}

A recent proliferation of air/ground/water unmanned vehicle
technologies has ever increased interests on deployment of intelligent
algorithms on embedded or mobile platforms. Among those technologies,
computer vision algorithms are getting more attentions primarily
because those mobile platforms have limited payload to carry other
active sensors and, without increasing much cost, installation of a
monocular camera even stereo rigs would increase the usefulness of a
mobile platform. For example, instead of just bare flight function
with video recording, an unmanned air vehicle (UAV) equipped with
object or feature following would make it more useful in the
application of monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on sports/movies/events,
many others.

@@

One of the dominant frameworks for online object tracking is one based
on the correlation filter that essentially solves a regression problem
in the frequency domain. This framework assumes that the target
information is given at the very first image frame like other online
tracking algorithms. Given this positive example for the regression
problem, a set of negative examples is collected around the initial,
target bounding box and represented as a circulant matrix
\cite{henriques2015high}. One can optimally solve this regression
problem using a ridge regression in a closed form. However, such a
solution involves in expensive matrix operations
$\mathcal{O}(n^{3})$. The correlation filter provides one with a much
cheaper solution, $\mathcal{O}(n\log n)$ over element-wise
multiplication in a frequecny domain
\cite{bolme2010visual,henriques2015high}. Due to such a reformulation,
a complete pipeline of an object tracker based on the correlation
filter can be easily implemented and run in an online fashion
efficiently. However, the vanilla form of such an online tracker is
prone to drift, and fails to track a target over a long period of
time. This is explained well by the dilemma of stability-plasticity in
updating appearance model in that the appearance model will be
overfitted to only the images used to train and a compromise on the
frequency of updating the model is carefully implemented
\cite{santner2010prost}.

{\it YoungWoo: Need to clean up the following paragraphs until Section
  2.}

The tracking-by-detection methods have recently used extensively as a
robust, powerful, and highly discriminative vision-based, object
tracking method replacing the preceding, generative object tracking
methods that primarily concerned about learning the appearance of the
target.

The recent examples of the tracking-by-detection algorithms include
Tracking-Learning-Detection \cite{kalal2012tracking}, Multiple
Instance Learning \cite{babenko2009visual}, Correlation Filter based
trackers \cite{bolme2010visual,henriques2015high}, and Struck
\cite{hare2012efficient}. These tracking-by-detection methods learn
the model of the target's appearance on the fly while discriminating
the target from the background.

{\it Burak: It isn't clear what you're getting at here}

{\it YoungWoo : Here, I am making an introduction
into the tracking-by-detection paradigm. I wanted to explain that they improve tracking as they learn an appearance model representative of the background and object. However, as I want to point out, the tracking-by-detection algorithms can be unfeasible as training a robust classifier can be costly. } Learning
an object-specific classifier in an online manner can better handle
challenging scenarios with the cost of increased complexity.

To train a (binary) classifier to detect the target at every frame,
the classifier needs positive and negative examples. In a typical set
up, a positive example is assumed to be given whereas a set of
negative examples can be randomly collected from the background around
the given positive example. Such a typical setup for a
tracking-by-detection method might have two issues related to its
performance: Firstly, the appearance of the randomly sampled negative
examples might be highly correlated with that of positive one,
resulting in ambiguous boundary between positive and negative
classes. Secondly for a real-time tracking, such a setup would not be
feasible for the practice because the number of training data
gradually increases. Due to these issues, most of the
tracking-by-detection methods focus on efficiently handling
incremental update of the learned classifier and on collecting a
small, but informative negative examples.

{\it Burak: Why do we even mention these issues? Is this somehow
  related to what we did for this paper?}

{\it YoungWoo : They are not related at all, however, I wanted to give a brief idea about tracking-by-detection challenges. I feel like the text in between line 147 - 187 can precede the paragraph starting at line 122. Do you think it makes sense? This way, we give an introduction on tracking-by-detection.}

\begin{comment}
However, there can be two issues in this framework. First,
the randomly collected samples can have large correlation resulting in
a weak classifier. Also, such framework is not feasible for real-time
tracking as the number of samples gradually increases. Most of the
tracking-by-detection algorithms focus on efficient incremental update
of a classifier together with more useful background sampling.
\end{comment}

An object tracking method based on the correlation filter in frequency
domain has gained attention due to its fast computation.

\begin{comment}
{\it Burak: This is not entirely true. If this is the case, people
  including us don't have to invent their own, other than just using
  KCF.}

Frequency domain correlation filter based trackers in the
tracking-by-detection paradigm has recently seen growing popularity
due to its superior computation and robustness to geometric and
photometric variations. 
\end{comment}

{\it YoungWoo: We'll have to mention why such an online tracker is
  still attractive over any DNN-based counterparts.}

@@

{\it YoungWoo : I think the following paragraph and paragraph in between line 118-143 give a brief idea about CF and KCF. We can probably combine them in a single paragraph followed by our contributions.}

The first correlation filter tracker proposed by
\cite{bolme2010visual} focused on learning and detection in the
frequency domain. The idea was to minimize the sum of squared error in
the frequency domain. Hence, the convolution in the original domain is
avoided, instead, element-wise multiplication is needed in the
frequency domain. This way, it achieved promising performance at 700
Hz. On the other hand, the MOSSE tracker failed in cases with rapidly
changing background as it learns the filter using a single template
and accommodates single channel features. Later on, the MOSSE tracker
was improved by using the circularly shifted background patches in an
efficient way by utilizing the theorem that Discrete Fourier Transform
of a circulant matrix gives us diagonalized circulant matrix
\cite{henriques2012exploiting,henriques2015high}. In the same work,
the authors integrated kernelization concept into the detection and
learning steps to improve tracking
accuracy. \cite{galoogahi2013multi,henriques2015high} extended the
correlation filter trackers with single channel features to
multi-channel features. They employed the color and shape features in
a simple framework by summing the correlation of the test and learned
feature channels elements. There a few major drawbacks of the
correlation filter trackers although they outperformed the other
discriminative trackers with superior computation. First, due to the
nature of correlation filters it is limited to a region of interest
which is typically 2-3 times larger than the target. Considering a
larger ROI not only increases the computational burden but also leads
to further spatial information loss with the fixed template size. For
this reason, its performance degrades in fast motion cases as the ROI
may not contain the target. Second, the correlation filter lacks scale
adaptation ability since it only estimates the translation of the
target. Later studies focused on improving the latter issue by
proposing scale candidates where each scale is assigned a confidence
by performing detection on the shrinked or enlarged the ROI
\cite{li2014scale,tang2015multi,bibi2015multi,ma2015long}. Another
group of studies employ the part-based correlation filter trackers to
better adapt to the scale changes
\cite{liu2015real,akin2016deformable}. The sensitivity to fast motion
is generally handled in the long-term target tracking framework where
track reinilization module is triggered when the target is lost
\cite{ma2015long,de2015board,li2016monocular}.

@@

\item \textbf{Single-Target Tracking in High-Speed} To be practical,
  the execution time of an object tracking is important. We proposed a
  new object tracking algorithm that is a collection of kernelized
  correlation filters (KCF). Each of KCFs is designed to address two
  challenges of object tracking: scale and translation. We also
  incorporate a Bayes filter to prevent from being drift.

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications for embedded systems in that most of the embedded systems
already includes image acquisition pipeline and a tremendous amount of
progresses on research has been made for many areas. However, to
successfully deploy a computer vision algorithm on any existing
embedded systems, a vision algorithm needs to satisfy some criteria:
minimal, manual intervention after deployment and small footprint of
computing resource consumption and on executable code, with the
assumption of reasonably good performance. To this end, in this paper,
we propose an ensemble of the kernelized correlation filters (KCF), we
call {\it E}nKCF, for a single-target object tracking. In particular,
we developed a committee of KCFs to specifically address the
scale-change and dynamic maneuver of the target over frames. In
addition, we devised a Bayes filter for a smooth transition between
individual KCFs' executions. To minimize the effect of drifting, we
also developed another algorithm that detects target-lost, uses an
existing object proposal method (e.g., ``Edge Box'') to re-detect the
lost target, and re-initializes the previous tracking for a long-term
tracking. To verify the usefulness of the proposed method, we compared
the performance of ours to those of the existing online tracking
methods. Experimental results showed that the performance of ours are
72.53\% for precision on 20 pixels and 52.90\% for success rate for
OTB100 data, and 55.71\% and 41.71\% for UAV123 data. These results
confirmed that our method outperformed the existing ones over 5\% on
precision on 20 pixels and 10-20\% on AUC on average. Our
implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps),
DCF (457 fps), and STC (350 fps) for UAV123.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
\begin{itemize}
\item YoungWoo: Clean up the introduction
\item Burak: Clean up the technical section: EnKCF, KCF, and Particle Filter
\item Burak: You'll have a conclusion whether we'll have the re-detection part by Friday night.
\item By Monday, we'll have a draft ready to submit.
\end{itemize}

A recent proliferation of air/ground/water unmanned vehicle
technologies has ever increased interests on deployment of intelligent
algorithms on embedded or mobile platforms. Among those technologies,
computer vision algorithms are getting more attentions primarily
because those mobile platforms have limited payload to carry other
active sensors than a lightweight, monocular camera and, without
increasing much cost, installation of a monocular camera even stereo
rigs would increase the usefulness of a mobile platform. For example,
instead of having just bare flight function with video recording, an
unmanned air vehicle (UAV) equipped with object or feature following
would make it more useful in the application of
monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on sports/movies/events,
many others.

@@

One of the dominant frameworks for online object tracking is the
correlation filter that essentially solves a single-target tracking
problem as a regression problem in the frequency domain. This
framework assumes that the target location is given at the very first
image frame like other online tracking algorithms
\cite{smeulders2014survey}. Given this positive example for the
regression problem, a set of negative examples is collected around the
initial, target bounding box and represented as a circulant matrix
\cite{henriques2015high}. One can optimally solve this regression
problem using a ridge regression in a closed form. However, such a
solution involves in expensive matrix operations
$\mathcal{O}(n^{3})$. The correlation filter provides one with a much
cheaper solution, $\mathcal{O}(n\log n)$ over element-wise
multiplication in a frequecny domain
\cite{bolme2010visual,henriques2015high}. Thank to this reformulation,
a complete pipeline of an object tracker based on the correlation
filter can be easily implemented and run very efficiently in an online
fashion. In fact, a variant of the correlation filter, kernelized
correlation filter with multi-channel features, outperformed other
state-of-the-art tracking algorithms in VOT15 challenge, in terms of
run-time and tracking accuracy. However, the vanilla form of such an
online tracker is prone to drift, and fails to track a target over a
long period of time primarily \cite{henriques2015high} because of the
dilemma of stability-plasticity in updating appearance model, where
the appearance model will be overfitted to only the images used to
train and a compromise on the frequency of updating the model is
carefully implemented \cite{santner2010prost}. For example, a naive
way of handling a scale change of a target could reduce the run-time
performance from 300 to 100 fps. A seemingly obvious way of addressing
the scale change is to scan the region of interest (ROI) with
templates in different dimensions based on pre-defined scale ratios to
find the target
\cite{henriques2015high,tang2015multi,ma2015long,bibi2015multi,li2014scale}. However,
because of computational nature of correlation filter, this approach
would just increase the computational complexity of tracking by
running detection with multiple possibilities.

Another way of handling the scale change for the correlation filter
based approach is to find a correct scale at a location where a target
highly likely appears \cite{zhang2014fast}. In particular, they uses
the MOSSE tracker to estimate a target's translation. The scale is
updated in a naive way where the confidence map is used to determine
the scale change between successive frames.

For instance, their method assumes similar scale in between two
consecutive frames given similar confidences. With this simple method,
we do not need to run detection on different ROIs at a given frame and
perform tracking at $\geq300$ fps. In this study, we propose the use
of Ensemble KCFs in an intuitive way to perform robust scale-adaptive
tracking at more than $300$ fps. Our approach is inspired by
\cite{ma2015long} where two KCFs are employed as translation and scale
filters. It first estimates translation using the translation filter
learned on \textit{target}$+$\textit{background} area. Then, the scale
filter learned on the \textit{target} area is used to estimate new
scale of the target at the estimated position. Application of
translation and scale filter at each frame reduces run-time
performance ($\leq50 fps$) as we need to run detection on each scale
candidate and perform training on both filters. Similarly, we learn
three different correlation filters specializing on different aspects
of tracking and addresses the weakness of each other, resulting in
more robust tracking. We name these filters as
\textit{target}+\textit{small background} translation filter
($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
\textit{target}+\textit{large background} translation filter
($R_{t}^{L}$). Unlike \cite{ma2015long}, by running a single filter at
each frame, we can achieve the targeted operation frame rate. The
fig.~\ref{fig:Filters} shows the size of the ROIs associated with
$R_{t}^{S}$, $R_{t}^{L}$, and $R_{s}$ in addition to the hanning
windows assigned and desired Gaussian responses assigned to each one.

@@

@@

\item \textbf{Novel Single-Target Tracking in High-Speed for Long-Term
  Tracking} To be practical, the execution time of an object tracking
  is important. We proposed a new object tracking algorithm that is a
  collection of kernelized correlation filters (KCF). Each of KCFs is
  designed to address two challenges of object tracking: scale and
  translation. We also incorporate a Bayes filter to prevent from
  being drift.
